Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-10 jss/article.tex
[skip ci] update examples.

>>>>

Recent years have witnessed a dramatic increase in new technologies for
interrogating the activity levels of various cellular components on a
genome-wide scale, including genomic, epigenomic, transcriptomic, and proteomic
information \citep{hawkins2010next}. Integrating these
heterogeneous datasets provides more biological insights than performing
separate analyses.

For instance, international consortia such as The Cancer Genome Atlas (TCGA)
have launched large-scale
initiatives to characterize multiple types of cancer at different levels
(genomic, transcriptomic, epigenomic, etc.) on several hundreds of samples.
These integrative studies have already led to the identification of novel cancer
genes \citep{mclendon2008comprehensive}.

Glioblastoma multiforme (GBM) is the most malignant form of gliomas, and despite
intense investigation of this disease in the past decades, most patients with
GBM die within approximately 15 months of diagnosis \citep{maher2001malignant}.
